Proposal full title \\ Proposal Acronym

### 2001-10-15 drafts/IST/PartA.tex
Some minor changes and grammar check.
svn path=/trunk/; revision=1550

juste be cut\&paste.

@@

In almost two years, the biggest barriers for Free Software development have
been raised by hosting facilities which provide most of the mandatory tools
that free software developers need for everyday tasks such as Bug tracking,
mailing lists, Project management... But although there are many hosting

@@

facilities but will focus an the ease of configuration and installation that
all current ones lack. \\

@@

and adoption in European countries for non english speakers.\\ Finally SICHA
will introduce support for cooperation in hosting platforms, that will be a
first step to the creation of networks of hosting facilities. 

@@

989 characters... (846 non white) \\

@@

The first one will be a next generation easy to install and international
hosting facility. It will provide a web frontend to a number of tools now 
mandatory for software development (user/groups rights management, bug tracking, mailing lists and forums...). 
The main idea between its design is to make it transparently distributed.
At each step of its development, we will focus on the ease of installation and configuration.  will also provide support for internationalization to help dissemination and adoption in European countries for non english speakers.\\
The second one will provide a generic description of
an hosting facility. With that tool we want to allow different kinds of facility
to communicate with each other. It will help to develop tools to facilitate
migrations between hosting facilities. This part is more oriented on data formats and tools to exchange informations between hosting facilities. It may
be released as an individual package from the first part.\\

@@

\subsection*{Description of the work (max 2000 characters)} to be written

@@

The hosting facility is composed of two main parts, the frontend and the
backend. The first one is the code base that interacts with the user and that
will implement services that are not provided by external software. The backend
will link the Database (filled by the frontend) to external software which

@@

install on a virgin machine or a machine already used for other

@@

multiple purposes, our focus will be on development hosting facilities. \\

To achieve this goal, we will 
1 redesing existing hosting architectures such as Savannah and Picolibre 
  so that they may be packaged, installed and taylored easily; 
2 integrate multilanguage support to these platforms and implement support
  versions for portuguese, german, spanish, english and french;
3 define common data types and representation between the two types of
  platform with possible interaction with other platform via the CoopX project;
4 introduce functionalities to import/export informations from one site to
  another, based on this common data representation;
5 test and deploy over wide area network at least three sites in three out
	of four participating countries.
%1445/1224 chars need check and more description
\subsection*{Milestones and expected result (max 500 characters)}
PM 3: specification of new hosting architecture
PM 6: specification of common data formats
PM 9: V1 of savannah with new design 1 language version
PM12: V1 of picolibre with new design
      V2 of savannah with support for at least 2 languages and import/export
PM15: V2 of picolibre with multilingual support for at least 2 languages and
      import/export functionalities
PM18: deployment of redesigned platform in 3 countries, 
      dissemination of the project results by a Debian package.
%496/408
\section*{A4 Cost Summary}
%% will look at that later
\textbf{This must be discussed very soon}
\rotatebox{90}{
\begin{tabular}{c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
Participant Role(CO/P) & Participant Number & Linked to Contractor No &
Participant Short Name & Number of Person - Months & Personnel Costs &
Durable Equipment & Consumables & Travel and subsitence & Computing &
External assistance & Other Costs & Knowledge protection on Costs & 
Overhead Costs & Total Costs & Requested Contribution from the Commision &
Eligibility (Y/No)\\
\end{tabular}
}
\end{document}

>>>>

just be cut\&paste.

@@

In the last two years, the biggest barriers for Free Software development have
been raised by hosting facilities which provide most of the essential tools
that free software developers need for everyday tasks such as bug tracking,
mailing lists, project management... But even though there are many hosting

@@

facilities ---and more--- but will focus on the ease of configuration and
installation that all current ones lack. \\

@@

and adoption for non-English speakers, in European countries.\\
Finally, SICHA will introduce support for cooperation in hosting platforms;
that will be a first step to the creation of networks of hosting facilities. 

@@

998 characters... (846 non white) \\

@@

The first one will be a next generation, easy to install, international
hosting facility. It will provide a web front-end to a number of tools now 
essential for software development (user/groups rights management, bug
tracking, mailing lists and forums...). 
The main idea guiding its design is to make it transparently distributed.
At each step of its development, we will focus on the ease of installation and
configuration. We will also provide support for internationalization, to help
its dissemination and adoption in European countries for non-English speakers.
The second part of the project will provide a specification for a generic
description of a hosting facility. With that tool we want to allow different
kinds of facilities to communicate with each other. It will help develop tools
to facilitate migrations among hosting facilities. This part is more oriented
towards data formats and tools to exchange information among hosting
servers. The two parts of the project may be released as separate packages,
but its joint development will benefit both.\\

@@

\subsection*{Description of the work (max 2000 characters)}

@@

The hosting facility is composed of two main parts, the front-end and the
back-end. The first one is the code base that interacts with the user and that
will implement services that are not provided by external software. The
back-end will link the database (filled by the front-end) to external
software which

@@

install on a brand new machine or a machine already used for other

@@

various purposes, our focus will be on development hosting facilities. \\

To achieve the project's goal, we will: 
1 Re-desing existing hosting architectures such as Savannah and Picolibre 
  so that they may be packaged, installed and taylored easily; 
2 Integrate multi-language support to these platforms and implement support
  versions for Portuguese, German, Spanish, English and French;
3 Define common data types and representation between the two types of
  platform (Savannah and Picolibre) and open the possibility of interacting
  with other platforms via the CoopX project;
4 Introduce utilities to import/export information from one site to
  another, based on this common data representation;
5 Test and deploy the system over a wide area network; at least at three
  different sites from the group of four participant countries.
%1445/1224 chars need check and more description
\subsection*{Milestones and expected result (max 500 characters)}
PM 3: specification of new hosting architecture
PM 6: specification of common data formats
PM 9: V1 of Savannah with new design 1 language version
PM12: V1 of Picolibre with new design
      V2 of Savannah with support for at least 2 languages and import/export
PM15: V2 of Picolibre with multilingual support for at least 2 languages and
      import/export functionalities
PM18: deployment of redesigned platform in 3 countries, 
      dissemination of the project results through a Debian package.
%496/408
\section*{A4 Cost Summary}
%% will look at that later
\textbf{This must be discussed very soon}
\rotatebox{90}{
\begin{tabular}{c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
Participant Role(CO/P) & Participant Number & Linked to Contractor No &
Participant Short Name & Number of Person - Months & Personnel Costs &
Durable Equipment & Consumables & Travel and subsitence & Computing &
External assistance & Other Costs & Knowledge protection on Costs & 
Overhead Costs & Total Costs & Requested Contribution from the Commision &
Eligibility (Y/No)\\
\end{tabular}
}
\end{document}
